\newsection
\section*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ} %заголовок списка литературы

\begin{hyphenrules}{nohyphenation} %отключение переноса слов в содержании
  \begin{thebibliography}{10}

    \bibitem{javascript} Bessmertny, I. A. Systems of artificial intelligence: textbook. allowance for SPO / I. A. Bessmertny. — 2nd ed., corrected. and additional - M. : Yurayt Publishing House, 2018. - 130 p. – Текст : непосредственный.
    \bibitem{php} Gordeev, S. I. Organization of databases in 2 hours. Part 2: a textbook for universities / S. I. Gordeev, V. N. Voloshina. — 2nd ed., corrected. and additional - M. : Yurayt Publishing House, 2019. - 501p . – Текст : непосредственный.
    \bibitem{css} Zykov, S. V. Programming. Object-oriented approach: textbook and workshop for academic undergraduate students / S. V. Zykov. - M. : Yurayt Publishing House, 2019. - 155 p. – Текст : непосредственный.
    \bibitem{mysql}	Ivanov, V. M. Intelligent systems: textbook. manual for SPO / V. M. Ivanov; under scientific ed. A. N. Sesekina. - M. : Yurayt Publishing House, 2019. - 93 p. – Текст : непосредственный.
	\bibitem{CH}	Бином. Лаборатория знаний - М., 2005. - 472 c. – Текст : непосредственный.
	\bibitem{htmlcss}	Zhmud, V. A. Modeling of closed systems of automatic control: textbook. manual for academic undergraduate studies / V. A. Zhmud. — 2nd ed., corrected. and additional - M. : Yurayt Publishing House, 2019. - 128 p.– Текст : непосредственный.
	\bibitem{CH1} Васильев Алексей C\#. Объектно-ориентированное программирование; Питер - М., 2012. - 320 c. – Текст : непосредственный.
	\bibitem{CH2}  Ватсон Б. C\# 4.0 на примерах (C\# 4.0. How-To); БХВ-Петербург - М., 2011. - 608 c. – Текст : непосредственный.
	\bibitem{CH3} Ватсон Б. C\# 4.0 на примерах; БХВ-Петербург - М., 2010. - 139 c. – Текст : непосредственный.    
	\bibitem{SPO}	Gnidenko, I. G. Software development technology: textbook. manual for SPO / I. G.Gnidenko, F. F. Pavlov, D. Yu. Fedorov. - M. : Yurayt Publishing House, 2017. - 235 p – Текст : непосредственный.       
  \end{thebibliography}
\end{hyphenrules}
